---
title: "R Notebook"
output: html_notebook
---

Questions 2-5 below require the peacekeeping data set that we worked on in class, as well as this codebook (see the appendix):
http://web.worldbank.org/archive/website01241/WEB/IMAGES/INTERNAT.PDF

The class breakout instructions (including data download code) are here:
https://gist.github.com/diamonaj/3795bfc2e6349d00aa0ccfe14102858d

```{r}
# Importing relevant libraries
library(Matching)

# Importing the data
foo <- read.csv("https://course-resources.minerva.kgi.edu/uploaded_files/mke/00086677-3767/peace.csv")
                
# Extract relevant columns
## Class break-out code
foo <- foo[, c(6:8, 11:16, 99, 50, 114, 49, 52, 63, 136, 109, 126, 48, 160, 142, 10, 108)] # WHY were 52 and 108 not included here originally? Should I include them as per the past answer key code?

# Remove 2 rows with missing data (there are better ways to handle missing data)
foo <- foo[c(-19, -47), ]

# Check that all missing data is gone...
which(is.na(foo) == TRUE)

# Take a peek at the data set (identify the columns)
head(foo)


## Treatment is a binary version of "uncint": levels of UN intervention (i.e. "Enforcement," "None," "Observer," "PKO")
## Outcomes are "pbs2l": peacebuilding success 2 years after the war; and "pbs5l": peacebuilding success 5 years after the war 

```

(2) Replicate the analysis done to produce figure 8 in https://gking.harvard.edu/files/counterf.pdf -- EXCEPT instead of the original interaction term, add two other interaction terms: (exp*untype4) and (wardur*logcost).

# EXCEPT that this figure considers the implications of
# adding an interaction term (wardur * untype4) to the basic model. 
# I want you to consider the implications of adding the interaction term (logdead*untype4).
Show the marginal effects of UN peacekeeping as a function of war duration, as in the original figure. 

A few suggestions:
- Read the class breakout instructions above to get the data and relevant columns;
- If you are not clear on the model, read the relevant sections of the paper and focus on understanding Table 2;
- To plot the figure, you should use a strategy similar to the one we used in the statistics scavenger hunt, which was also used in a previous assignment (e.g., holding predictors at their means and looping through values of one variable to obtain treatment effects at different levels of the variable--you may want to review the answer key for that previous assignment.

```{r}
##############
# QUESTION 2 #
##############

# Original regression model  
glm.og <- glm(pbs2s3 ~ wartype + logcost + wardur + factnum + factnum2 + 
              trnsfcap + develop + exp + decade + treaty + untype4,
            data = foo, family = binomial)

# New regression model
glm.new <- glm(pbs2s3 ~ wartype + logcost + wardur + factnum + factnum2 + 
                     trnsfcap + develop + exp + decade + treaty + untype4 + 
                     I(exp*untype4) + I(wardur*logcost), 
                   data = foo, family = binomial)

mean.wartype <- mean(foo$wartype)
mean.logcost <- mean(foo$logcost)
mean.wardur <- mean(foo$wardur)
mean.factnum <- mean(foo$factnum)
mean.factnum2 <- mean(foo$factnum2)
mean.trnsfcap <- mean(foo$trnsfcap)
mean.develop <- mean(foo$develop)
mean.exp <- mean(foo$exp)
mean.decade <- mean(foo$decade)
mean.treaty <- mean(foo$treaty)

# Define function to  ... of regression model  
get_logit <- function(X, coef) {
  logit <- coef[1] + sum(coef[2:length(coef)]*X)
  return(exp(logit) / (1 + exp(logit)))
}

storage.original.treat <- rep(NA, length)
storage.original.control <- rep(NA, length)

# length <- nrow(foo)
length = 315

for (wardur in 1:length) {
  X.treat <- c(mean.wartype, mean.logcost, wardur, mean.factnum, mean.factnum2, 
               mean.trnsfcap, mean.develop, mean.exp, mean.decade, mean.treaty, 1)
  X.control <- c(mean.wartype, mean.logcost, wardur, mean.factnum, mean.factnum2, 
                 mean.trnsfcap, mean.develop, mean.exp, mean.decade, mean.treaty, 0)
  
  storage.original.treat[wardur]  <- get_logit(X.treat, coef(glm.og))
  storage.original.control[wardur]  <- get_logit(X.control, coef(glm.og))
}

original_y <- storage.original.treat - storage.original.control


storage.logcost.treat <- rep(NA, length)
storage.logcost.control <- rep(NA, length)

for (wardur in 1:length) {
  X.treat <- c(mean.wartype, mean.logcost, wardur, mean.factnum, mean.factnum2, 
               mean.trnsfcap, mean.develop, mean.exp, mean.decade, mean.treaty, 1, 
               mean.exp*1, wardur*mean.logcost) 
  X.control <- c(mean.wartype, mean.logcost, wardur, mean.factnum, mean.factnum2, 
                 mean.trnsfcap, mean.develop, mean.exp, mean.decade, mean.treaty, 0,
                 mean.exp*0, wardur*mean.logcost) # Or just x3 0, 0, 0 ?
  storage.logcost.treat[wardur]  <- get_logit(X.treat, coef(glm.new))
  storage.logcost.control[wardur]  <- get_logit(X.control, coef(glm.new))
}

logcost_y <- storage.logcost.treat - storage.logcost.control

plot(1:length, original_y, type = "l", lty = "dotted", ylim = c(0, 0.8), xlab = "Duration of wars in months", ylab = "Marginal effects of UN peacekeeping operations")
lines(1:length, logcost_y, col = "blue", ylim = c(0, 0.8))
# legend(1, 95, legend=c("Model with interaction terms", "Dotted: Original model"), col=c("black", "blue"), lty="dotted", cex=0.8)
text(x=120,  y=0.75,  "Model with interaction terms", cex=0.8, col="blue")
text(x=50,  y=0.58,  "Dotted: Original model", cex=0.8)
```

(3) Define treatment as below:
	Tr <- rep(0, length(foo$uncint))
	Tr[which(foo$uncint != 0] <- 1

	What does this mean? What is "treatment"?

```{r}
##############
# QUESTION 3 #
##############

Tr <- rep(0, length(foo$uncint))
Tr[which(foo$uncint != 0)] <- 1

head(Tr)

# Outputs a 122 (the length of foo/foo's column "uncint") "0"s (a numeric) -- this is a dataframe?
# Finds the indexes of all the values in foo's column "uncint" that are not equal to "0"/None and assigns a   1 to the same indexes in Tr
# In other words,  it classifies the different levels of UN intervention (i.e. "Enforcement," "None," "Observer," "PKO" as either treatment (1) or control (0).  All descriptors other than "None"--  "Enforcement," "None," and "Observers"--are assigned the value of 1; and "None" is considered no treatment and assigned the value of 0.  
# Note: the code should use "None" instead of "0" (and add a paranthese) in order for it to work as intended when finding the indexes in foo's uncint column. Hence, Tr[which(foo$uncint != 0)] <- 1 should be Tr[which(foo$uncint != "None")] <- 1 
```
